Delaying Bug Fixes is a Bad Idea?

### 2015-07-30 phaseDelay.tex
Updates from ShareLaTeX

\begin{figure}
{\small
\begin{center}
\begin{tabular}{r|rrrr|r}
& \multicolumn{4}{c}{Phase Requirements Issue Found }& ref\\
                &Requirements & Design & Code&  Test& ref\\\hline
 & 1& 5& 10& 50&~\cite{Boehm81}\\  
& 1 &3& 5& 37&?\\ 
&  1 &3& 7& 51& ?\\ 
& 1& 5 &33 &75& ? \\
& 1  &    & 10 & 40& ?\\ 
& 1   &    & 10 &  40& ?\\
&  1 & 20 & 45 & 250& ?\\  
&  1  &   5 &      & 50& ? \\\hline
mean             & 1 & 7.3 & 25.6 & 177\\
median           & 1 &  5  & 10   & 50.5 
\end{tabular}
\end{center}}
\caption{Sample of the Stecklein et al. literature; from~\cite{steck04}.}
\end{figure}

@@

\begin{figure}[!t] 
%\vspace{-1cm}
%\hspace{-0.35in}
\begin{center}
\includegraphics[width=3in]{img/b81.pdf}
 \end{center}
% ~\\~\\
%~\\~\\~\\

>>>>

\begin{figure}
{\small
\begin{center}
\begin{tabular}{r|rrrr|r}
& \multicolumn{4}{c}{Phase Requirements Issue Found }& ref\\
                &Requirements & Design & Code&  Test& ref\\\hline
 & 1& 6& 10& 70&~\cite{Boehm81}\\  
& 1 &3& 5& 37&?\\ 
&  1 &3& 7& 51& ?\\ 
& 1& 5 &33 &75& ? \\
& 1  &    & 10 & 40& ?\\ 
& 1   &    & 10 &  40& ?\\
&  1 & 20 & 45 & 250& ?\\  
&  1  &   5 &      & 50& ? \\\hline
mean             & 1 & 7.3 & 25.6 & 177\\
median           & 1 &  5  & 10   & 50.5 
\end{tabular}
\end{center}}
\caption{Sample of the Stecklein et al. literature; from~\cite{steck04}.}
\end{figure}

@@

\begin{figure}[!t]  
\begin{center}
\includegraphics[angle=270,width=3.5in]{img/b81.pdf}
 \end{center}
 \caption{From Boehm~\cite{Boehm81}. }\label{fig:cost-to-fix-tsp}
 \end{figure}
